---
title: "ds202_hw2"
author: "xiwang"
date: "02/05/19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#R commands

##Question 1

Today¡¯s temperature has a high of 15 and a low of -10 degree fahrenheit. Find the corresponding degress in celsius and storage it in a (single) vector named cel. Print the variable.

```{r}
f <- c(15,-10)
cel <- 5/9 * (f - 32)
cel
```

##Question 2

Create a vector of length 200. The odd entries should be 1 and even entries should be 0. Storage the created in a variable named vec200 and print.

```{r}
vec200 <- rep (c(1,0), length.out=200)
vec200
```

##Question 3

How many perfect squares are there between 1 and 1001? Storage the answer in a variable named numPerfect and print. 


```{r}
sqrt <- sqrt(1:1001)
round <- round (sqrt,digits = 0)
table <- as.data.frame(table(round))
numPerfect <-  length (table$round)
numPerfect
```

#Cars and mileage

## Question 1
What are the 3 most fuel-efficient models in terms of highway mileage? Storage the data frame (with 3 rows) containing all information of these three cars in a variable named top3 and print.

```{r}
library(ggplot2)
sort <- mpg[order(-mpg$hwy), ]
top3 <- head(sort,3)
top3
```

## Question 2
How many different compact models are included in this dataset? Storage the answer in a variable named numCompact and print.

```{r}
names (mpg)
summary (mpg$model)
table1 <- as.data.frame(table(mpg$model))
numCompact <-  length (table1$Var1)
numCompact
```



## Question 3
Create a scatterplot of hwy and cty and describe the relationship. Why are there so few points visible?

```{r}
plot((mpg$hwy),(mpg$cty))
```

##### There is positive relationship between hwy and cty variables
##### Plots refere to the types of cars in which some cars have the same value


## Question 4
Are cars in 2008 more fuel efficient than cars in 1999? Use graphs and summary statistics to answer this question.

```{r}
dathwy <- mpg$hwy

box<- boxplot((dathwy[mpg$year==1999]),(dathwy[mpg$year==2008]),names=c("1999","2008"))
h99 <- dathwy[mpg$year==1999]
h08 <- dathwy[mpg$year==2008]
summary (h99)
summary (h08)

```
##### According to the result, it shows 2008 more fuel efficient than cars in 1999.

